The Strucplot Framework---Visualizing Multi-way Contingency Tables

### 2005-09-28 trunk/vcd/inst/doc/strucplot.Rnw
- structable-indexing now using [] - replacement function for structables - vcdViewport-layout fixed (again), title_margins argument added - strucplots accept structables as gp argument
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@463 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

<<subsetting,results=verbatim>>=
hec
hec[["Male",]]
hec[[c("Male", "Brown"),]]
hec[["Male","Green"]]
@

@@

pushViewport(viewport(layout.pos.col = 1))
mosaic(hec[["Male"]], margins = c(top = 2, 0), sub = "Male", newpage = FALSE)
popViewport()

pushViewport(viewport(layout.pos.col = 2))
mosaic(hec[["Female"]], margins = c(top = 2, 0), sub = "Female", newpage = FALSE)
popViewport(2)
@

>>>>

<<subsetting,results=verbatim>>=
hec
hec["Male",]
hec[c("Male", "Brown"),]
hec["Male","Green"]
@

@@

pushViewport(viewport(layout.pos.col = 1))
mosaic(hec["Male"], margins = c(top = 2, 0), sub = "Male", newpage = FALSE)
popViewport()

pushViewport(viewport(layout.pos.col = 2))
mosaic(hec["Female"], margins = c(top = 2, 0), sub = "Female", newpage = FALSE)
popViewport(2)
@
